---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mapSenegal - Administrative Boundaries of Senegal 

<!-- badges: start -->
<!-- badges: end -->

The goal of mapSenegal is to provides access to administrative boundaries of 
Senegal at several levels (regions, departements, arrondissements and communes), 
These boundaries are based on 'GDAM'. The package also gives access to localities, 
universities, roads and health facilities locations.  base maps and 

## Installation

You can install the development version of mapSenegal with:

``` r
# install.packages("remotes")
remotes::install_github("rCarto/mapSenegal")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(mapSenegal)
library(mapsf)
reg <- sn_regions()
dep <- sn_departments()
mf_map(dep)
mf_map(reg, col = NA, lwd = 3, add = TRUE)
```
